Contracts for Contracts

### 2023-04-27 paper.tex
some thoughts

\todo{where to add message sender? proposed syntax:}
\begin{lstlisting}
  # ts1 @ f(x) returns z from sdr1 => ts2 @ g(a) returns c from sdr2
\end{lstlisting}
\begin{lstlisting}
  # f(x) returns z => g(a) returns c /\ f.msg.sender == g.msg.sender
\end{lstlisting}

@@

>>>>

\todo{where to add message sender? proposed syntax:}
\begin{lstlisting}
  # ts1 @ f(x) returns z from sdr1 => ts2 @ g(a) returns c from sdr2
\end{lstlisting}
\begin{lstlisting}
  # f(x) returns z => g(a) returns c /\ f.msg.sender == g.msg.sender
\end{lstlisting}
\wac{\texttt{msg.sender} is better tied with transaction. We can use ts1.msg.sender and I prefer to put the constraints in the side-cond. }

@@

\wac{I think the previous definition of contextual property $h ~> g$ means $\forall g, \exists h$ implicitly, i.e., for any $g$ called, there must exist one $h$ on the call stack. I cannot think of a use scenario where quantifiers on $h$ and $g$ are needed in practice.}
\wac{If we want to distinguish different call frames of $h$ and $g$, maybe it's better to design activation constraints for the contextual properties, e.g., \texttt{cond -> h ~> g}, meaning $h ~> g$ is only enforced when $cond$ is true (imply). ps: the special arrow is broken outside the listing environment. :(}
